### 2024-07-01 FinalThesis/Chapter_03/Manuscript_Support.tex
Publish PHD

\documentclass[abstract=on,10pt,a4paper,bibliography=totocnumbered]{article}
\usepackage[paper=a4paper,left=35mm,right=35mm,top=25mm,bottom=30mm]{geometry}
\usepackage[doublespacing]{setspace}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{colortbl}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{gensymb}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage[hidelinks]{hyperref}
\usepackage[nameinlink]{cleveref}
\usepackage{multirow}
\usepackage{arydshln}
\usepackage[flushleft]{threeparttable}
\usepackage{scalerel}
\usepackage{makecell}
\usepackage{ifthen}
\usepackage{tikz}
\usepackage{lineno}
\usetikzlibrary{svg.path}

%------------------------------------------------------------------------------
%  Bibtex vs Biblatex
%------------------------------------------------------------------------------
% While bibtex is very nice to use, it's insanely slow. I therefore work with
% bibtex until the final stage. Set the value below to "true" or "false" to pick
% which one should be used.
\newboolean{usebiblatex}
\setboolean{usebiblatex}{false}

% Depending on the question, the commands below will prepare the document
% accordingly
\ifthenelse{\boolean{usebiblatex}}{
  %-----------------------------------------------------------------------------
  %  If using biblatex
  %-----------------------------------------------------------------------------
  % Load required packages and refer to correct bibliography
  \usepackage{csquotes}
  \usepackage[
      backend=biber
    , style=apa          % To display Author-year in the text
    , natbib=true        % Necessary to use citep, etc.
    , hyperref=true      % To have clickable links in the references
    , useeditor=false    % Don't add editor to publications
    , sorting=ynt        % Sort by year, name, and title
    , uniquename=false   % Avoid that initials are put
  ]{biblatex}
  \addbibresource{Literature.bib}

  % To include author in link
  \DeclareFieldFormat{citehyperref}{%
  \DeclareFieldAlias{bibhyperref}{noformat}% Avoid nested links
  \bibhyperref{#1}}
  \DeclareFieldFormat{textcitehyperref}{%
  \DeclareFieldAlias{bibhyperref}{noformat}% Avoid nested links
  \bibhyperref{%
    #1%
    \ifbool{cbx:parens}
      {\bibcloseparen\global\boolfalse{cbx:parens}}
      {}}}
  \savebibmacro{cite}
  \savebibmacro{textcite}
  \renewbibmacro*{cite}{%
    \printtext[citehyperref]{%
      \restorebibmacro{cite}%
      \usebibmacro{cite}}}
  \renewbibmacro*{textcite}{%
    \ifboolexpr{
      ( not test {\iffieldundef{prenote}} and
        test {\ifnumequal{\value{citecount}}{1}} )
      or
      ( not test {\iffieldundef{postnote}} and
        test {\ifnumequal{\value{citecount}}{\value{citetotal}}} )
    }
      {\DeclareFieldAlias{textcitehyperref}{noformat}}
      {}%
    \printtext[textcitehyperref]{%
      \restorebibmacro{textcite}%
      \usebibmacro{textcite}}}

  % Remove editor form everything but books
  \AtEveryBibitem{%
   \ifentrytype{book}{}{%
    \clearname{editor}
   }
  }
}{
  %-----------------------------------------------------------------------------
  %  If using bibtex
  %-----------------------------------------------------------------------------
  % Load required packages and select citation style
  \usepackage[round]{natbib}
  \bibliographystyle{apalike}
}

%------------------------------------------------------------------------------
%	Some Styling
%------------------------------------------------------------------------------
% Link colors
\definecolor{linkcolor}{HTML}{000000}
\hypersetup{
  colorlinks = true,
  linkcolor  = linkcolor,
  urlcolor   = linkcolor,
  citecolor  = linkcolor,
}

% Changing the style of captions in figures etc.
\captionsetup{labelfont=bf, format=plain, font=small}

% Change how equations are referenced
\renewcommand{\theequation}{Equation \arabic{equation}}%

% Avoid skip when including text from external .tex file
\newcommand{\inputy}[1]{\input{#1}\unskip}

% For supplementary material
\newcommand{\beginappendix}{%
  \setcounter{table}{0}
  \renewcommand{\thetable}{S\arabic{table}}%
  \setcounter{figure}{0}
  \renewcommand{\thefigure}{S\arabic{figure}}%
  \setcounter{equation}{0}
  \renewcommand{\theequation}{Equation S\arabic{equation}}%
  \setcounter{section}{0}
  \renewcommand{\thesection}{A.\arabic{section}}%
}

%------------------------------------------------------------------------------
%  ORCID
%------------------------------------------------------------------------------
% Creating some TikZ styles
\tikzset{
  nonterminal/.style = {rectangle
    , minimum size = 6mm
    , very thick
    , draw = black!
  }
}

% Create the ORCID logo
\definecolor{orcidlogocol}{HTML}{A6CE39}
\tikzset{
  orcidlogo/.pic={
    \fill[orcidlogocol]
      svg{M256,128c0,70.7-57.3,128-128,128C57.3,256,0,198.7,0,128C0,57.3,57.3
        ,0,128,0C198.7,0,256,57.3,256,128z};
    \fill[white]
      svg{M86.3,186.2H70.9V79.1h15.4v48.4V186.2z}
      svg{M108.9,79.1h41.6c39.6,0,57,28.3,57,53.6c0,27.5-21.5,53.6-56.8
        ,53.6h-41.8V79.1z M124.3,172.4h24.5c34.9,0,42.9-26.5
        ,42.9-39.7c0-21.5-13.7-39.7-43.7-39.7h-23.7V172.4z}
      svg{M88.7,56.8c0,5.5-4.5,10.1-10.1,10.1c-5.6,0-10.1-4.6-10.1-10.1c0-5.6
      ,4.5-10.1,10.1-10.1C84.2,46.7,88.7,51.3,88.7,56.8z};
  }
}

% Command to create the ORCID
\newcommand\orcid[1]{\href{https://orcid.org/#1}{\mbox{\scalerel*{
\begin{tikzpicture}[yscale=-1,transform shape]
  \pic{orcidlogo};
\end{tikzpicture}
}{|}}}}

%------------------------------------------------------------------------------
%	Titlepage: Header
%------------------------------------------------------------------------------
\title{\textbf{Appendix}\\ Individual-Based Dispersal Simulations to Study
Dynamic Connectivity in Seasonal Landscapes}

% List of Authors
\author{
  David D. Hofmann\textsuperscript{1,2,\S} \orcid{0000-0003-3477-4365} \and
  Dominik M. Behr\textsuperscript{1,2} \orcid{0000-0001-7378-8538} \and
  John W. McNutt\textsuperscript{2} \and
  Arpat Ozgul\textsuperscript{1, 2} \orcid{0000-0001-7477-2642} \and
  Gabriele Cozzi\textsuperscript{1,2} \orcid{0000-0002-1744-1940}
}

% Reduce spacing between authors
\makeatletter
\def\and{%
  \end{tabular}%
  \hskip -0.5em \@plus.17fil\relax
  \begin{tabular}[t]{c}}
\makeatother

% Current Date
% \date{\today}

% And here the masterpiece begins
\begin{document}

% Change page numbering
\pagenumbering{gobble}

% Create Titlepage
\maketitle

%------------------------------------------------------------------------------
%	Titlepage: Additional Info
%------------------------------------------------------------------------------
\begin{flushleft}

\vspace{0.5cm}

\textsuperscript{1} Department of Evolutionary Biology and Environmental
Studies, University of Zurich, Winterthurerstrasse 190, 8057 Zurich,
Switzerland.

\textsuperscript{2} Botswana Predator Conservation Program, Wild Entrust,
Private Bag 13, Maun, Botswana.

\textsuperscript{\S} Corresponding author: \href{mailto://david.hofmann2@uzh.ch}{david.hofmann2@uzh.ch}

\vspace{4cm}

\textbf{Running Title:} Simulating Dispersal in Seasonal Landscapes

\vspace{0.5cm}

\textbf{Keywords:} African wild dog, Connectivity, Dispersal, Dynamism,
Individual-based, Lycaon pictus, Okavango Delta, Seasonality

\end{flushleft}

%------------------------------------------------------------------------------
%	Main Text
%------------------------------------------------------------------------------
\newpage

\onehalfspacing
\tableofcontents
\doublespacing

% Change page numbering
\pagenumbering{arabic}

% Create linenumbers
% \linenumbers

% Change to appendix counters
\appendix
\beginappendix

%------------------------------------------------------------------------------
%	Appendix S1: Pan Mapping
%------------------------------------------------------------------------------
\newpage
\section{Pan Mapping}
\subsection{Satellite Product Overview}

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width = \textwidth]{Figures/Pan}
  \caption{A pan as it can be found in Botswana right after the rainy season.
  This particular pan is comparably small at around 10 meters in diameter. Some
  of these pans dry out quickly, whereas others provide a source of water for
  the entire dry-season. Here, two spotted hyenas (\textit{Crocuta crocuta})
  take a quick bath.}
  \label{Pan}
 \end{center}
\end{figure}

@@

\noindent Our goal was to produce dynamically updated pan-maps that we could
overlay with GPS data of dispersing African wild dogs. Since GPS data was
collected between 2015 and 2022, this implied that satellite data needed to be
available for the same period. At first glance, all satellite products appeared
to meet this criteria. However, Landsat 7's scan-line detector had been failing
since May 31, 2003, introducing data gaps between adjacent tiles, thus rendering
the product virtually unusable for our purposes (but see \citealp{Storey.2005}).
Sentinel 2 and Landsat 8, by contrast, appeared as viable alternatives, as both
of them spanned the desired period and did not exhibit any device failures.

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width = \textwidth]{Figures/PanMapping.pdf}
  \caption{Example of a \textit{wet pan} and \textit{dryland} training polygon
  digitized on Google Earth. The extent of water can easily be gauged at the
  maximum zoom level in Google Earth. While the dryland polygon in this case
  covered an area that is seasonally covered by water, we placed other dryland
  polygons in areas that were never inundated. However, to ensure reliable
  differentiation between wet and dry pans, we included several dryland polygons
  located in dry pans.}
  \label{PanMapping}
 \end{center}
\end{figure}

@@

We downloaded Landsat 8 imagery through Google Earth Engine using the
\texttt{rgee} \texttt{R}-package \citep{Aybar.2024} and used the associated
quality band to mask pixels classified as clouds or shadows. We also computed
several normalized difference indices (NDs), as listed in \Cref{ND}. To download
Sentinel 2 data, we used the \texttt{sen2r} \texttt{R}-package
\citep{Ranghetti.2020} which provides a standardized interface to download and
process Sentinel 2 imagery from the European Space Agency's data hub. Sentinel 2
data are available as either top-of-the-atmosphere (TOA, level 1C) or
bottom-of-the-atmosphere (BOA, level 2A) reflectance values. In analyses where
temporal trends are considered, the use of BOA reflectances is recommended, as
differences in reflectance properties due to atmospheric conditions are
accounted for \citep{Gilabert.1994, Vermote.2008, Chraibi.2022}. However, a
large portion of the publicly available Sentinel 2 data has not yet been
processed from level 1C to level 2A, requiring researchers to apply the
corrections themselves. Fortunately, the European Space Agency provides the
correction tool \texttt{sen2cor} for free \citep{Main-Knorn.2017}, and this tool
has been integrated into the \texttt{R}-package \texttt{sen2r}
\citep{Ranghetti.2020}. We therefore applied the necessary corrections after
download for any product that hadn't already been corrected. Furthermore, we
used Sentinel 2's ``Scene Classification Map'', to remove pixels classified as
either clouds or shadows. Finally, we computed the same ND-indices as for
Landsat 8 (\Cref{ND}).

@@

To train a land-cover classifier, we generated 3'000 random points within
training polygons following a stratified equal random sampling scheme
\citep{Shetty.2021}. That is, we ensured that 1'000 random points were sampled
per training category. Stratified random sampling was necessary to ensure that
wet-pans, our category of interest, was sampled frequently enough, as it
represented a minority class, only making up of
(\inputy{GeneralMetrics/PercentageTrainingWetpan}\%) the total training area.
Stratified equal random sampling has been shown to provide good class-level
accuracy for minority classes \citep{Shetty.2021}, so we deemed this approach
suitable for our purposes. We also kept track of the dates of the underlying
polygons from which random points were generated. At each random point, we then
extracted reflectance values of Sentinel 2 and Landsat 8 data that temporally
aligned with the date assigned to the random point (\Cref{Reflectances}a). For
instance, if a random point fell into a polygon that was digitized using a
Google Earth image generated on Aug 18, 2018, we extracted values from the
Sentinel 2 and Landsat 8 layers that were closest to that date. Finally, we
parameterized a Random Forest (RF) classifier using the \texttt{R}-package
\texttt{randomForest} \citep{Cutler.2024} and a Classification and Regression
Tree (CART) classifier using the \texttt{R}-package \texttt{rpart}
\citep{Therneau.2024b}. In both cases, we included all bands, as well as derived
ND-indices (\Cref{ND}) as explanatory covariates. We visualized the decision
trees for the CART classifiers (\Cref{Reflectances}b) and variable importance
for the RF models (\Cref{Reflectances}c) to investigate the importance of
different bands or indices in separating the three classes. To compute variable
importance we used the \texttt{R}-package \texttt{caret} \citep{Kuhn.2008}.

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width = \textwidth]{Figures/Reflectances.png}
  \caption{Reflectance properties of the Landsat 8 (a1) and Sentinel 2 (a2)
  bands and NDs at the extracted training points for each of the three
  categories (colored). Based on extracted reflectance values we parametrized
  Classification and Regression Tree models (b1 and b2) as well as Random Forest
  models (c1 and c2).}
  \label{Reflectances}
 \end{center}
\end{figure}

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width = \textwidth]{Figures/ClassificationValidation.png}
  \caption{Confusion matrices (a) and derived performance metrics (b) for the
  CART and RF classifiers for both the Landsat 8 and Sentinel 2 datasets.}
  \label{ClassificationValidation}
 \end{center}
\end{figure}

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width = \textwidth]{Figures/MovingWindows.png}
  \caption{To reduce the number of Sentinel 2 tiles that we needed to download,
  we generated a monthly updated spatio-temporal moving window that comprised
  all GPS data of dispersing wild dogs (black dots) during the respective month,
  buffered by a 100 km radius. Based on the so created moving windows (in blue),
  we identified all overlapping Sentinel 2 tiles (tiles in gray) that we needed
  to download each month, which resulted in a total of 2,226 tiles.}
  \label{MovingWindows}
 \end{center}
\end{figure}

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width = \textwidth]{Figures/MovingWindows2.png}
  \caption{Moving windows and associated tiles facetted by months.}
  \label{MovingWindows2}
 \end{center}
\end{figure}

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width = 0.75\textwidth]{Figures/Moonlight.png}
  \caption{Moonlight intensity (illumination) as estimated from the
  \texttt{moonlit} package \citep{Smielak.2023} in \texttt{R} calculated for a
  couple of example timestamps in 2023.}
  \label{Moonlight}
 \end{center}
\end{figure}

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width = \textwidth]{Figures/Light.pdf}
  \caption{Schematic illustration of how we categorized steps into \textit{dark}
  and \textit{bright} steps. First, we used the \texttt{suncalc} and
  \texttt{moonlit} packages to obtain estimates of the sun-angle and moon
  illumination at 5 minute intervals for each date of interest. Whenever the sun
  angle was $\leq $ -18\degree, we deemed the respective period to be at night.
  A night was either bright (moon illumination $>$ 0.02 of maximum illumination)
  or dark (moon illumination $\leq$ 0.02 of maximum illumination). Any other
  period was considered to provide enough illumination for wild dogs to move and
  therefore considered as bright. Since each step covered a time-span of
  approximately four hours, we defined a step as bright if at least 25\% (i.e.,
  one hour) of it occurred during a bright period. The gray arrows represent
  some example steps that are categorized as bright (light gray) or dark (dark
  gray).}
  \label{Light}
 \end{center}
\end{figure}

@@

\begin{table}[htbp]
 \begin{center}
  \caption{Estimates obtained from the \textbf{simple} (no interactions)
  integrated step-selection models fitted using \textbf{static} covariates. GPS
  Data was either pooled across seasons (labeled ``all'') or split into dry and
  wet season. Only underlined covariates differed between the static and dynamic
  configurations.}
  \label{ModelsStaticSimple}
   \begin{threeparttable}
   \inputy{Figures/MovementModelStaticSimple.tex}
   \end{threeparttable}
 \end{center}
\end{table}

\begin{table}[htbp]
 \begin{center}
  \caption{Estimates obtained from the \textbf{simple} (no interactions)
  integrated step-selection models fitted using \textbf{dynamic} covariates. GPS
  Data was either pooled across seasons (labeled ``all'') or split into dry and
  wet season. Only underlined covariates differed between the static and dynamic
  configurations.}
  \label{ModelsDynamicSimple}
   \begin{threeparttable}
   \inputy{Figures/MovementModelDynamicSimple.tex}
   \end{threeparttable}
 \end{center}
\end{table}

\begin{table}[htbp]
 \begin{center}
  \caption{Estimates obtained from the \textbf{full} (with interactions)
  integrated step-selection models fitted using \textbf{static} covariates. GPS
  Data was either pooled across seasons (labeled ``all'') or split into dry and
  wet season. Only underlined covariates differed between the static and dynamic
  configurations.}
  \label{ModelsStaticFull}
   \begin{threeparttable}
   \inputy{Figures/MovementModelStaticFull.tex}
   \end{threeparttable}
 \end{center}
\end{table}

\begin{table}[htbp]
 \begin{center}
  \caption{Estimates obtained from the \textbf{full} (no interactions)
  integrated step-selection models fitted using \textbf{dynamic} covariates. GPS
  Data was either pooled across seasons (labeled ``all'') or split into dry and
  wet season. Only underlined covariates differed between the static and dynamic
  configurations.}
  \label{ModelsDynamicFull}
   \begin{threeparttable}
   \inputy{Figures/MovementModelDynamicFull.tex}
   \end{threeparttable}
 \end{center}
\end{table}

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width = \textwidth]{Figures/Stability.png}
  \caption{Results from the integrated step-selection models when considering
  different numbers of random steps. Results are shown for the simple and full
  model for both all configurations of fitting covariates (static vs dry) and
  model seasons (all vs. wet + dry).}
  \label{Stability}
 \end{center}
\end{figure}

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width = \textwidth]{Figures/MovementModelInterpretation.png}
  \caption{Relative selection scores (RSS) with respect to environmental
  covariates. RSS scores were computed by comparing a location $x_1$ with
  average conditions to a location $x_2$ with average conditions but the
  respective covariate varied between its minimum and maximum observed value.
  Confidence intervals overlapped substantially, hence we omitted them from the
  figure to simplify with the interpretation of the differences among
  configurations.}
  \label{MovementModelInterpretation}
 \end{center}
\end{figure}

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width = \textwidth]{Figures/RankCorrelationNumberSteps.png}
  \caption{Illustration how the Spearman's rank correlation changes when the
  number of random steps per stratum is varied from 5 to 100 (facettes). The
  y-axis shows the frequency at which the observed step was assigned the rank
  indicated on the x-axis. A low rank indicates that the observed step was
  assigned a high probability of being chosen. The better the prediction, the
  more frequently the observed step should be assigned a low rank, thus
  resulting in negative Spearman's rank-correlation. However, it is obvious that
  the metric heavily depends on the number of random steps per stratum. If there
  are only a few random steps, the correlation is more likely to be negative.
  The show patterns are based on simulated data.}
  \label{RankCorrelationNumberSteps}
 \end{center}
\end{figure}

\newpage
\begingroup
\singlespacing
\ifthenelse{\boolean{usebiblatex}}{
  \begin{refcontext}[sorting=nyt]
  \printbibliography
  \end{refcontext}
}{
  \bibliography{LiteratureBibtex}
}
\endgroup
\end{document}

>>>>

\documentclass[../FinalThesis.tex]{subfiles}
\begin{document}

\newpage

%------------------------------------------------------------------------------
%	Appendix S1: Pan Mapping
%------------------------------------------------------------------------------
\newpage
\section{Pan Mapping}
\label{PanMappingApproach}

\subsection{Satellite Product Overview}

@@

\begin{figure}[htpb]
 \begin{center}
  \includegraphics[width = \textwidth]{Figures/Pan}
  \caption{A pan as it can be found in Botswana right after the rainy season.
  This particular pan is comparably small at around 10 meters in diameter. Some
  of these pans dry out quickly, whereas others provide a source of water for
  the entire dry-season. Here, two spotted hyenas (\textit{Crocuta crocuta})
  take a quick bath.}
  \label{Pan}
 \end{center}
\end{figure}

@@

\noindent Our goal was to produce dynamically updated pan-maps that we could
overlay with GPS data of dispersing African wild dogs. Since most GPS data were
collected between 2015 and 2022, this implied that satellite data needed to be
available for the same period. At first glance, all satellite products appeared
to meet this criteria. However, Landsat 7's scan-line detector had been failing
since May 31, 2003, introducing data gaps between adjacent tiles, thus rendering
the product virtually unusable for our purposes (but see \citealp{Storey.2005}).
Sentinel 2 and Landsat 8, by contrast, appeared as viable alternatives, as both
of them spanned the desired period and did not exhibit any device failures.

@@

\begin{figure}[htpb]
 \begin{center}
  \includegraphics[width = \textwidth]{Figures/PanMapping.pdf}
  \caption{Example of a \textit{wet pan} and \textit{dryland} training polygon
  digitized on Google Earth. The extent of water can easily be gauged at the
  maximum zoom level in Google Earth. While the dryland polygon in this case
  covered an area that is seasonally covered by water, we placed other dryland
  polygons in areas that were never inundated. However, to ensure reliable
  differentiation between wet and dry pans, we included several dryland polygons
  located in dry pans.}
  \label{PanMapping}
 \end{center}
\end{figure}

@@

We downloaded Landsat 8 imagery through Google Earth Engine using the
\texttt{rgee} \texttt{R}-package \citep{Aybar.2024} and used the associated
quality band to mask pixels classified as clouds or shadows. We also computed
several normalized difference indices (NDs), as listed in \Cref{ND}. To download
Sentinel 2 data, we used the \texttt{sen2r} \texttt{R}-package
\citep{Ranghetti.2020} which provides a standardized interface to download and
process Sentinel 2 imagery from the European Space Agency's data hub. Sentinel 2
data are available as either top-of-the-atmosphere (TOA, level 1C) or
bottom-of-the-atmosphere (BOA, level 2A) reflectance values. In analyses where
temporal trends are considered, the use of BOA reflectances is recommended, as
differences in reflectance properties due to atmospheric conditions are
accounted for \citep{Gilabert.1994, Vermote.2008, Chraibi.2022}. However, a
large portion of the publicly available Sentinel 2 data has not yet been
processed from level 1C to level 2A, requiring researchers to apply the
corrections themselves. Fortunately, the European Space Agency provides the
correction tool \texttt{sen2cor} for free \citep{Main-Knorn.2017}, which has
been integrated into the \texttt{R}-package \texttt{sen2r}
\citep{Ranghetti.2020}. We therefore applied the necessary corrections after
download for any product that hadn't already been corrected. Furthermore, we
used Sentinel 2's scene classification, to remove pixels classified as either
clouds or shadows. Finally, we computed the same ND-indices as for Landsat 8
(\Cref{ND}).

@@

To train a land-cover classifier, we generated 3,000 random points within
training polygons following a stratified equal random sampling scheme
\citep{Shetty.2021}. That is, we ensured that 1,000 random points were sampled
per training category. Stratified random sampling was necessary to ensure that
wet-pans, our category of interest, was sampled frequently enough, as it
represented a minority class, only making up of
(\inputy{GeneralMetrics/PercentageTrainingWetpan}\%) the total training area.
Stratified equal random sampling has been shown to provide good class-level
accuracy for minority classes \citep{Shetty.2021}, so we deemed this approach
suitable for our purposes. We also kept track of the dates of the underlying
polygons from which random points were generated. At each random point, we then
extracted reflectance values of Sentinel 2 and Landsat 8 data that temporally
aligned with the date assigned to the random point (\Cref{Reflectances}a). For
instance, if a random point fell into a polygon that was digitized using a
Google Earth image generated on Aug 18, 2018, we extracted values from the
Sentinel 2 and Landsat 8 layers that were closest to that date. Finally, we
parameterized a Random Forest (RF) classifier using the \texttt{R}-package
\texttt{randomForest} \citep{Cutler.2024} and a Classification and Regression
Tree (CART) classifier using the \texttt{R}-package \texttt{rpart}
\citep{Therneau.2024b}. In both cases, we included all bands, as well as derived
ND-indices (\Cref{ND}) as explanatory covariates. We visualized the decision
trees for the CART classifiers (\Cref{Reflectances}b) and variable importance
for the RF models (\Cref{Reflectances}c) to investigate the importance of
different bands or indices in separating the three classes. To compute variable
importance we used the \texttt{R}-package \texttt{caret} \citep{Kuhn.2008}.

\begin{figure}[htpb]
 \begin{center}
  \includegraphics[width = \textwidth]{Figures/Reflectances.png}
  \caption{Reflectance properties of the Landsat 8 (a1) and Sentinel 2 (a2)
  bands and NDs at the extracted training points for each of the three
  categories (colored). Based on extracted reflectance values we parametrized
  Classification and Regression Tree models (b1 and b2) as well as Random Forest
  models (c1 and c2).}
  \label{Reflectances}
 \end{center}
\end{figure}

@@

\begin{figure}[htpb]
 \begin{center}
  \includegraphics[width = \textwidth]{Figures/ClassificationValidation.png}
  \caption{Confusion matrices (a) and derived performance metrics (b) for the
  CART and RF classifiers for both the Landsat 8 and Sentinel 2 datasets.}
  \label{ClassificationValidation}
 \end{center}
\end{figure}

@@

\begin{figure}[htpb]
 \begin{center}
  \includegraphics[width = \textwidth]{Figures/MovingWindows.png}
  \caption{To reduce the number of Sentinel 2 tiles that we needed to download,
  we generated a monthly updated spatio-temporal moving window that comprised
  all GPS data of dispersing wild dogs (black dots) during the respective month,
  buffered by a 100 km radius. Based on the so created moving windows (in blue),
  we identified all overlapping Sentinel 2 tiles (tiles in gray) that we needed
  to download each month, which resulted in a total of 2,226 tiles.}
  \label{MovingWindows}
 \end{center}
\end{figure}

\begin{figure}[htpb]
 \begin{center}
  \includegraphics[width = \textwidth]{Figures/MovingWindows2.png}
  \caption{This figure shows the moving windows generated for each month, as
  well as the underlying GPS data and overlapping Sentinel 2 tiles that we
  ultimately downloaded and combined into monthly composites.}
  \label{MovingWindows2}
 \end{center}
\end{figure}

@@

\begin{figure}[htpb]
 \begin{center}
  \includegraphics[width = 0.75\textwidth]{Figures/Moonlight.png}
  \caption{Moonlight intensity as estimated from the \texttt{moonlit} package
  \citep{Smielak.2023} in \texttt{R}, calculated for several example timestamps
  in 2023.}
  \label{Moonlight}
 \end{center}
\end{figure}

@@

\begin{figure}[htpb]
 \begin{center}
  \includegraphics[width = \textwidth]{Figures/Light.pdf}
  \caption{Schematic illustration of how we categorized steps into \textit{dark}
  and \textit{bright} steps. First, we used the \texttt{suncalc} and
  \texttt{moonlit} packages to obtain estimates of the sun-angle and moon
  illumination at 5 minute intervals for each date of interest. Whenever the sun
  angle was $\leq $ -18\degree, we deemed the respective period to be at night.
  A night was either bright (moon illumination $>$ 0.02 of maximum illumination)
  or dark (moon illumination $\leq$ 0.02 of maximum illumination). Any other
  period was considered to provide enough illumination for wild dogs to move and
  therefore considered as bright. Since each step covered a time-span of
  approximately four hours, we defined a step as bright if at least 25\% (i.e.,
  one hour) of it occurred during a bright period. The gray arrows represent
  some example steps that are categorized as bright (light gray) or dark (dark
  gray).}
  \label{Light}
 \end{center}
\end{figure}

@@

\begin{table}[htpb]
 \begin{center}
  \caption{Estimates obtained using the \textbf{simple model formula} (no
  interactions) and \textbf{static} covariates. GPS Data were either pooled
  across seasons (labeled ``all'') or split into wet and dry season. Only
  underlined covariates differed between the static and dynamic configurations.}
  \label{ModelsStaticSimple}
   \begin{threeparttable}
   \inputy{Figures/MovementModelStaticSimple.tex}
   \end{threeparttable}
 \end{center}
\end{table}

\begin{table}[htpb]
 \begin{center}
  \caption{Estimates obtained using the \textbf{simple model formula} (no
  interactions) and \textbf{dynamic} covariates. GPS Data were either pooled
  across seasons (labeled ``all'') or split into wet and dry season. Only
  underlined covariates differed between the static and dynamic configurations.}
  \label{ModelsDynamicSimple}
   \begin{threeparttable}
   \inputy{Figures/MovementModelDynamicSimple.tex}
   \end{threeparttable}
 \end{center}
\end{table}

\begin{table}[htpb]
 \begin{center}
  \caption{Estimates obtained using the \textbf{complex model formula} (with
  interactions) and \textbf{static} covariates. GPS Data were either pooled
  across seasons (labeled ``all'') or split into wet and dry season. Only
  underlined covariates differed between the static and dynamic configurations.}
  \label{ModelsStaticFull}
   \begin{threeparttable}
   \inputy{Figures/MovementModelStaticFull.tex}
   \end{threeparttable}
 \end{center}
\end{table}

\begin{table}[htpb]
 \begin{center}
  \caption{Estimates obtained using the \textbf{complex model formula} (with
  interactions) and \textbf{dynamic} covariates. GPS Data were either pooled
  across seasons (labeled ``all'') or split into wet and dry season. Only
  underlined covariates differed between the static and dynamic configurations.}
  \label{ModelsDynamicFull}
   \begin{threeparttable}
   \inputy{Figures/MovementModelDynamicFull.tex}
   \end{threeparttable}
 \end{center}
\end{table}

@@

\begin{figure}[htpb]
 \begin{center}
  \includegraphics[width = \textwidth]{Figures/Stability.png}
  \caption{Results from the integrated step-selection models when considering
  different numbers of random steps. Results are shown for the simple and
  complex formulas for all configurations of fitting covariates (static vs dry)
  and model seasons (all vs. wet + dry). For some design combinations, models
  failed to converge and thus dropped from the figure.}
  \label{Stability}
 \end{center}
\end{figure}

@@

\begin{figure}[htpb]
 \begin{center}
  \includegraphics[width = \textwidth]{Figures/MovementModelInterpretation.png}
  \caption{Relative selection scores (RSS) with respect to environmental
  covariates. RSS scores were computed by comparing a location $x_1$ with
  average conditions to a location $x_2$ with average conditions but the
  respective covariate varied between its minimum and maximum observed value.
  Confidence intervals overlapped substantially, hence we omitted them from the
  figure to simplify the interpretation of the differences among
  configurations.}
  \label{MovementModelInterpretation}
 \end{center}
\end{figure}

@@

\begin{figure}[htpb]
 \begin{center}
  \includegraphics[width = \textwidth]{Figures/RankCorrelationNumberSteps.png}
  \caption{Illustration how the Spearman's rank correlation changes when the
  number of random steps per stratum is varied from 5 to 100 (facettes). The
  y-axis shows the frequency at which the observed step was assigned the rank
  indicated on the x-axis. A low rank indicates that the observed step was
  assigned a high probability of being chosen. The better the prediction, the
  more frequently the observed step should be assigned a low rank, thus
  resulting in negative Spearman's rank-correlation. However, it is obvious that
  the metric heavily depends on the number of random steps per stratum. If there
  are only a few random steps, the correlation is more likely to be negative.
  The show patterns are based on simulated data.}
  \label{RankCorrelationNumberSteps}
 \end{center}
\end{figure}

\ifSubfilesClassLoaded{%
  \newpage
  \begin{singlespacing}
  \ifthenelse{\boolean{usebiblatex}}{
    \begin{refcontext}[sorting=nyt]
    \printbibliography
    \end{refcontext}
  } {
    \bibliography{../LiteratureBibtex}%
  }
\end{singlespacing}
}{}

\end{document}
